---
title: "Assignment 5"
author: "Nick Hall"
date: "5/3/2020"
output: html_document
---



1) 
a)

```{r}
(-2.3187 + -1.3678) * 10
```

b)
```{r}
0.265621 * 10
```

c) The model only gives predictions it does not supply you with the causality. So infering causality fom this model would just lead you astray.

d) We would expect the sign to be positive because with a normal good when income increases so does the demand, which would also increase the price of the normal good.


2)
a)
```{r}
setwd("C:/Users/nickr/OneDrive/Documents/ECON 487/Assignment02/Data")
df <- read.csv("oj.csv")

dom_data <- subset(df, brand == "dominicks")
quantile <- quantile(dom_data$INCOME)
quantile
```

2b)
```{r}
income_data <- dom_data[order(dom_data$INCOME),]
q1 <- income_data[income_data$INCOME <= quantile[2],]
q2 <- income_data[income_data$INCOME > quantile[2] & income_data$INCOME <= quantile[3],]
q3 <- income_data[income_data$INCOME > quantile[3] & income_data$INCOME <= quantile[4],]
q4 <- income_data[income_data$INCOME > quantile[4] & income_data$INCOME <= quantile[5],]

q1_avgSale <- mean(q1$logmove)
q2_avgSale <- mean(q2$logmove)
q3_avgSale <- mean(q3$logmove)
q4_avgSale <- mean(q4$logmove)

q1_avgSale
q2_avgSale
q3_avgSale
q4_avgSale
```

2c)
```{r}
q1_mse <- mean((q1$logmove - q1_avgSale)^2)
q2_mse <- mean((q2$logmove - q2_avgSale)^2)
q3_mse <- mean((q3$logmove - q3_avgSale)^2)
q4_mse <- mean((q4$logmove - q4_avgSale)^2)

q1_mse
q2_mse
q3_mse
q4_mse
```

2d) The third quantile had the lowest MSE. This lets us know that within this quantile it had the least spread about the mean.

2e)The first quantile had the largest MSE. This lets us know that within this quantile it had the largest spread about the mean.